Diagnostic Plots

### 2024-07-29 pre_print_manuscript.qmd
Moderators plots converted to grobs to reduce file size

### Examining the effects of a new trial upon belief in the effects of self-talk interventions
To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Sample size was simulated as 10, 20, 40, 80, 160, 320, 640, 1282, 2560, and 5120[^6] with a 50:50 allocation to either self-talk intervention or control conditions, and we varied the sample effect size as an SMD of 0, 0.2, 0.4, 0.6, 0.8, and 1.0 reflecting a range from no effect of self-talk interventions to a large  effect. In each combination of sample size and true effect size we set the sample parameters to  the SMD and its corresponding sampling variance was calculated and then included as a single observation in a Bayesian random effects meta-analysis where the priors was set informatively for the intervention effects, and were set to be default weakly regularising for the heterogeneity (i.e., $\tau$)[^7]. Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], reported in their Table 1, using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009]. We assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$. The prior for heterogeneity was set as the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$. This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values. We fit each model using four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations.

@@

### Updating the prior esitmate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies
For all the groups/conditions in studies identified in our updated searches effect sizes were calculated as SMDs dependent on the design of the study. Firstly, all were signed such that a positive effect indicated that the self-talk intervention was favoured. For studies utilising a pretest-posttest-control comparison design we calculated the SMD between groups/conditions using the pooled pre-test standard deviation as per Morris [-@morrisEstimatingEffectSizes2008]. For post-test only control comparison designs we calculated the SMD between groups/conditions based upon the pooled post-test standard deviation. Lastly, for single arm within group pre-post (or control-intervention) designs we calculated the SMD from pre- to post-intervention using the pre-test standard deviation.

@@

## Main model
```{r}
targets::tar_load(main_model)
targets::tar_load(tidy_main_model)
targets::tar_load(main_model_logBF_curve)
```

@@

## Moderators
```{r}
targets::tar_load(tidy_motor_demands_model)
targets::tar_load(tidy_selftalk_content_model)
targets::tar_load(tidy_matching_model)
targets::tar_load(tidy_task_novelty_model)
targets::tar_load(tidy_training_model)
```

@@

>>>>

To begin with we examined through simulation what impact a single new trial might have had upon shifting belief in the prior estimate yielded by the meta-analysis of Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. Sample size was simulated as 10, 20, 40, 80, 160, 320, 640, 1282, 2560, and 5120[^6] with a 50:50 allocation to either self-talk intervention or control conditions, and we varied the sample effect size as an SMD of 0, 0.2, 0.4, 0.6, 0.8, and 1.0 reflecting a range from no effect of self-talk interventions to a large  effect. In each combination of sample size and true effect size we set the sample parameters to  the SMD and its corresponding sampling variance was calculated and then included as a single observation in a Bayesian random effects meta-analysis where the priors was set informatively for the intervention effects, and were set to be default weakly regularising for the heterogeneity (i.e., $\tau$)[^7]. Intervention effects were set with priors based on the effect estimates from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011], reported in their Table 1, using a $t$-distribution ($t(k,\mu,\sigma)$) with $k-2$ degrees of freedom [@higginsReevaluationRandomeffectsMetaanalysis2009]. We assumed $k$ to be the number of effects included in the models reported by Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011]. The prior for the intervention effect was set directly on the model intercept i.e., $t(60, 0.48, 0.05)$. The prior for heterogeneity was set as the default weakly regularising prior in `brms`; a half-$t$-distribution with $\mu=0$, $\sigma=2.5$, and $k=3$. This constrained the prior to only allow positively signed values for $\tau$ though over a wide range of possible values. We fit each model using four Monte Carlo Markov Chains each with 2000 warmup and 6000 sampling iterations.

@@

### Updating the prior estimate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies
For all the groups/conditions in studies identified in our updated searches effect sizes were calculated as SMDs dependent on the design of the study. Firstly, all were signed such that a positive effect indicated that the self-talk intervention was favoured. For studies utilising a pretest-posttest-control comparison design we calculated the SMD between groups/conditions using the pooled pre-test standard deviation as per Morris [-@morrisEstimatingEffectSizes2008]. For post-test only control comparison designs we calculated the SMD between groups/conditions based upon the pooled post-test standard deviation. Lastly, for single arm within group pre-post (or control-intervention) designs we calculated the SMD from pre- to post-intervention using the pre-test standard deviation.

@@

## Examining the effects of a new trial upon belief in the effects of self-talk interventions

## Updating the prior estimate from Hatzigeorgiadis et al. [-@hatzigeorgiadisSelfTalkSportsPerformance2011] with newer studies

### Main model
```{r}
targets::tar_load(main_model)
targets::tar_load(tidy_main_model)
targets::tar_load(main_model_logBF_curve)
```

@@

### Moderators
```{r}
targets::tar_load(tidy_motor_demands_model)
targets::tar_load(tidy_selftalk_content_model)
targets::tar_load(tidy_matching_model)
targets::tar_load(tidy_task_novelty_model)
targets::tar_load(tidy_training_model)
```

@@

## Examining the quality of the evidence and potential questionable research practices
